Case Study: RNA-Seq Differential Analysis

### 2018-03-13 datasets/RNA-Seq/RNA-Seq.Rmd
Don't save plot as png in Rmd

```{r, meancov-diag-scatter, fig.width=4.5, fig.height=3.5}
gp <- rank_scatter(geneExp, pvalue = "pval", covariate = "ind_covariate") +
    ggtitle("Mean coverage as independent covariate") +
    xlab("Mean Expression")
ggsave("temp.png", gp, width = 4.5, height = 3.5)
```

>>>>

```{r, meancov-diag-scatter, fig.width=4.5, fig.height=3.5}
rank_scatter(geneExp, pvalue = "pval", covariate = "ind_covariate") +
    ggtitle("Mean coverage as independent covariate") +
    xlab("Mean Expression")
```
